Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-26 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Check in

Only the ``Start a session'' and ``Explore collections of other friends'' actions 
are not found in the graph model as these are stored in the PostgreSQL relational
database system.

Two scores are used to determine the weight of a user's preference:
\begin{itemize}
\item Experience. This value depends on the score and is a value 
between 0 and 100. 
% More details needed? Is done by a Fuzzy Inference System but I think
% the description would take to much space.

@@

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window, a screen capture of
this interface is shown in figure \ref{fig:top-users}.

@@

The three versions of the EvoDrawing web application were deployed to the
Heroku cloud service with the same configuration: using the
Heroku Free option with a 512 MB of RAM, adding only the GrapheneDB and RedisTOGO plug-ins.
Table \ref{tab:params} shows the parameters used for the evolutionary algorithm. The graph database 
system used in the implementation was Neo4J as it was allready available as a plug-in in Heroku, is well documented
and a scalable solution \cite{miller2013graph,holzschuher2013performance}.

@@

% Anuncements
At the start of each of the experiments, a call to participation was promoted through social networks
particularly on Facebook and Twitter social networks.
It is important to note that volunteers needed to log-in in to facebook and give permissions to the 
web application in order to participate, in thi case there were no anonymous volunteers. This permited the automatic access to
each participant's social network and enabled the system to store a local copy of those friends participating.
Another experiment is needed to see the effect this requirement has on participation.

>>>>

Only the ``Start a session'' and ``Explore collections of other friends'' actions 
are not reflected in the graph model since they are stored instead in the PostgreSQL relational
database system. % because... - JJ

Two scores are used to determine the weight of a user's preference:
\begin{itemize}
\item Experience. This value depends on the score and is a value 
between 0 and 100. 
% More details needed? Is done by a Fuzzy Inference System but I think
% the description would take to much space.
% Better a small description than nothing. If you need space, some
% sections above are maybe a bit too verbose - JJ

@@

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window. A screen capture of
this interface is shown in figure \ref{fig:top-users}.

@@

The three versions of the EvoDrawing web application were deployed to the
Heroku cloud service with the same configuration: using the
Heroku Free option with a 512 MB of RAM, adding only the GrapheneDB and RedisTOGO plug-ins.
Table \ref{tab:params} shows the parameters used for the evolutionary algorithm. The graph database 
system used in the implementation was Neo4J as it was already available as a plug-in in Heroku, is well documented
and a scalable solution \cite{miller2013graph,holzschuher2013performance}.

@@

% Anuncements
At the start of every experiment, a call to participation was issued
through social networks, 
particularly on Facebook and Twitter.
It is important to note that volunteers needed to log-in to Facebook and give permissions to the 
web application in order to participate, in this case there were no anonymous volunteers. This enabled the automatic access to
each participant's social network and enabled the system to store a local copy of those friends participating.
However, another experiment would be needed to see the effect this
requirement has on participation, since we are not dealing with it in
this paper.
